R Markdown Features

### 2018-07-23 1062_class/anthro_final/article.Rmd
up

---
title: "開源社群"
subtitle: "發展、運作以及與資本主義的互動"
author: "廖永賦$^1$"
output:
  bookdown::pdf_document2:
    number_sections: TRUE
    toc: TRUE
    includes:
      in_header: header.tex
    latex_engine: xelatex
urlcolor: blue
always_allow_html: yes
bibliography: anthro.bib
csl: apa_ch.csl
link-citations: yes
---

@@

$\\$  $\\$  $\\$ $\\$  [^1]

[^1]: 系級：心理三  \ \ 學號：B04207003

>>>>

---
title: "開源社群"
subtitle: "發展、運作以及與資本主義的互動"
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B04207003}"
output:
  bookdown::pdf_document2:
    number_sections: TRUE
    toc: TRUE
    includes:
      in_header: header.tex
    latex_engine: xelatex
urlcolor: blue
always_allow_html: yes
bibliography: anthro.bib
csl: apa_ch.csl
link-citations: yes
---

@@

### 2018-07-23 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```{yaml}
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt 
geometry: a5paper, headheight=0pt, margin=0.4in
---
```

@@

## PDF Output2 {-}
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---
```

@@

# Beamer Slide (PDF)

>>>>

You may need to attatch an additional `header.tex` and set `latex_engine` to `xelatex` for PDF documents containing multibite characters (e.g. Chinese). Read more about  [header.txt](#pdf-header).
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt 
geometry: a5paper, headheight=0pt, margin=0.4in
---
```

@@

## PDF Output2 {-}
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
author: "廖永賦\\thanks{組別：3 ~~ 系級：心理三 ~~ 學號：B00000000}"
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---
```

@@

# Beamer Slide
